\documentclass[12pt,a4paper]{article}
\usepackage[NoDate]{currvita}
\usepackage{mflogo}
\usepackage{hyperref}

\begin{document}
\begin{cv}{Jure \v{Z}bontar}
\noindent \emph{Curriculum Vitae}

\begin{cvlist}{}
\item[Address] Jure \v{Z}bontar \\
Raku\v{s}eva 26 \\
1000 Ljubljana \\
Slovenia

\item[Telephone] 
+1 917 633 9170 (US) \\
+386 41 911 372 (Slovenian)

\item[Email] jure.zbontar@gmail.com

\item[Skype] jzbontar

\item[Born] May 28, 1985, in Ljubljana, Slovenia
\item[Citizenship] Slovenian

\end{cvlist}

\begin{cvlist}{Education}
\item[2008 - present] PhD student \\
Faculty of Computer and Information Science \\
University of Ljubljana \\
Slovenia \\
GPA: 9.909 / 10

\item[2004 - 2008] BSc in Computer Science and Mathematics \\
Faculty of Computer and Information Science \\
University of Ljubljana \\
Slovenia \\
GPA: 9.538 / 10

\end{cvlist}


\begin{cvlist}{Professional Positions}
\item[2010 - present] Teaching Assistant, Bioinformatics Laboratory  \\
Faculty of Computer and Information Science \\
University of Ljubljana

\item[2008 - 2010] Teaching Assistant, Artificial Intelligence Laboratory \\
Faculty of Computer and Information Science \\
University of Ljubljana

\item[2007 - 2008] Information Systems Laboratory \\
Faculty of Computer and Information Science \\
University of Ljubljana

\end{cvlist}

\begin{cvlist}{Research Visits}
\item[Jan - Aug 2014] The Courant Institute of Mathematical Sciences \\
New York University \\
New York, NY 10003, USA \\
Mentor: Yann LeCun (\href{mailto:yann@cs.nyu.edu}{yann@cs.nyu.edu})
\end{cvlist}

\begin{cvlist}{Consulting}
\item[2013] CTB/McGraw-Hill \\
Implement system for automatic short answer scoring \\
\url{https://bitbucket.org/jzbontar/asap} \\
Contact: Michelle Barrett (\href{mailto:michelle_barrett@ctb.com}{michelle\_barrett@ctb.com})
\end{cvlist}


\subsection*{Teaching Activities}

\subsubsection*{Summer Schools}
The Faculty of Computer and Information Science in Ljubljana organizes
summer schools each year. I was the main organizer of the Machine Learning
Summer School in 2012 and 2013. The summer school is a gentle introduction
for undergraduate students focusing on the practical aspects of applying
machine learning to solve real world problems.

\subsubsection*{Teaching Assistant}
I teach 10 hours of lectures per week where I'm in charge of setting up the
exercises and homework assignments.

\begin{cvlist}{}
\item[2010 - 2012] Programming I
\item[2009] Algorithms and Data Structures
\item[2009] Artificial Intelligence
\end{cvlist}

\subsubsection*{Awards}
\begin{cvlist}{}
\item[2013] Best Teaching Assistant Award (based on student voting) \\
Faculty of Computer and Information Science \\
University of Ljubljana 

\end{cvlist}

\subsection*{Programming Competitions}
During my undergraduate years I enjoyed solving algorithmic problems. I entered
as many programming competitions as I possibly could. The lessons learned
had a great impact on my programming style and my way of thinking and solving problems.

\begin{cvlist}{}
\item[2009] Open Krakow Team Programming Challenge
\item[2008 - 2010] Entered Many TopCoder Competitions
\item[2008] ACM Central European Regional Contest
\item[2006 - 2008] ACM Slovenian Regional Contest
\item[2006 - 2010] Spent a lot of time on \url{http://uva.onlinejudge.org/} online judge
\end{cvlist}

\subsection*{Machine Learning Competitions}
Machine learning competitions probably take up most of my free time.
They are perfect for testing new ideas and comparing them to established
methods. I have learned many valuable lessons about how to make learning
algorithm behave well on real datasets. It's really exciting to see the machine
learning approach beat human benchmarks and hand engineering.

\begin{cvlist}{}
\item[2013 \quad 5th / 249] The Marinexplore and Cornell University Whale Detection
Challenge\footnotemark[1], \\
\url{http://www.kaggle.com/c/whale-detection-challenge}
\item[2012 \quad 1st / 126] Topical Classification of Biomedical Research Papers,
JRS 2012 Data Mining Competition\footnotemark[2], \\
\url{http://tunedit.org/challenge/JRS12Contest}
\item[2012 \quad 2nd / 91] EMC Israel Data Science Challenge\footnotemark[2], \\
\url{http://www.kaggle.com/c/emc-data-science}
\item[2012 \quad 2nd / 156] The Hewlett Foundation: Short Answer Scoring
Competition\footnotemark[1], \\
\url{http://www.kaggle.com/c/asap-sas}
\item[2011 \quad 1st / 104] Algorithm for Optimal Job Sceduling and Task
Allocation under Constraints\footnotemark[1] \\
\url{http://tunedit.org/challenge/job-scheduling}
\item[2010 \quad 1st / 22] Forecast Eurovision Voting\footnotemark[1], \\
\url{http://www.kaggle.com/c/Eurovision2010}
\end{cvlist}

\footnotetext[1]{Entered competition alone.}
\footnotetext[2]{Team leader.}

\subsection*{Completed Online Courses}
When I am not competing on Kaggle I am probably completing some online course.
The quality of some of the courses is absolutely amazing. The proliferation of
online courses has definitely played a role in my education. In the past few
years I have completed the following online courses:

\begin{cvlist}{}
\item[Coursera] 
\begin{itemize}
\item Machine Learning (Andrew Ng)
\item Neural Networks for Machine Learning (Geoffrey Hinton)
\item Probabilistic Graphical Models (Daphne Koller)
\item Writing in the Sciences (Kristin Sainani)
\end{itemize}

\item[Udacity] 
\begin{itemize}
\item Introduction to Parallel Programming (John Owens, David Luebke)
\item Introduction to Artificial Intelligence (Sebastian Thrun, Peter Norvig)
\end{itemize}

\item[Stanford] 
\begin{itemize}
\item EE263: Introduction to Linear Dynamical Systems (Stephen Boyd)
\item CS229: Machine Learning (Andrew Ng)
\item CS294A: Deep Learning and Unsupervised Feature Learning (Andrew Ng)
\end{itemize}

\item[Caltech] 
\begin{itemize}
\item Learning From Data (Yaser Abu-Mostafa)
\end{itemize}

\end{cvlist}

\subsection*{Programming Skills}
I really like programming. During my career I tried many different
programming languages from C, C++, Java and Go to LISP, Haskell, OCaml,
Erlang and Prolog. I also tried web programming with JavaScript, PHP and
ActionScript. Today, most of my code is written in Python (with NumPy,
Theano and scikit-learn) and Lua (with Torch). If my code is not running fast enough,
I like to speed it up with Cython, CUDA or C.

\end{cv}
\end{document}
